%% start of file `template.tex'.
%% Copyright 2006-2010 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper]{moderncv}
\usepackage{bibentry}
\usepackage[T1]{fontenc}
\usepackage{color}
%\usepackage[]{babel}
% moderncv themes
\moderncvtheme[green]{classic}
\usepackage[utf8]{inputenc}


% adjust the page margins
\usepackage[scale=0.92]{geometry}

\firstname{Noé}
\familyname{Gaumont}
\title{Ph.D. student at Université Pierre et Marie Curie} 
%\extrainfo{Permis B}

\address{13 rue Gustave Simonet}{ 94200 Ivry-sur-Seine} % optional, remove the line
%if not wanted
\mobile{06.77.79.86.28} % optional, remove the line if not
%wanted

\email{noe.gaumont@lip6.fr}
%\photo[72pt]{"image"}


\nopagenumbers{} 

\begin{document}
\maketitle
\vspace{-1.2cm}

\section{Professional Experience}
\cventry{Since October 2013} {Ph.D. student} {Université Pierre et Marie Curie}{}{in the ComplexNetwork team, LIP6}
{
\textit{Subject}: Community detection in link streams. Link stream provide a new way to understand temporal networks.
A link stream is a sequence of timed interactions between two entities, like email exchanges.
In this context, a community should be a dense sub-stream, \emph{e.g.} a discussion instead of a group of
friends in the case of mails.
}
\vspace*{0.2cm}
\cventry{Feb 2013 - July 2013}{Internship}{Thales Air System in the Innovation Lab}{Rungis}{}{Study and optimization of flight plan predictions on specific way-points.\newline \textit{Key concepts:} machine learning, data extrapolation. \textit{Languages:} C++, R.}%

\cventry{Sept 2011 - Feb 2012}{Internship}{Commissariat à l'énergie atomique (\textbf{CEA})}{Brétigny-sur-Orge}{}{Creation of an algorithm able to generate quadrilateral mesh under a vector field constraint and geometric constraints.
\textit{Key concepts}: paving mesh generation, finite element. \textit{Language}: C++.}

%\cventry{Jan 2009 - Feb 2009}{Worker internship}{Sealed Air - quality department}{\'Epernon}{}{Product control within the scope of quality check and communication with clients.\newline}%

%\cvline{April 2010 - Aug 2010}{Exchange program in Germany at the Technische Universität Hamburg-Harburg (TUHH).\newline Introduction to the finite element method and to the structural aspect of planes.}

\section{Education}
\cventry{Sept 2008 - July 2013}{Engineering school}{Université de Technologie de Compiègne}{}{in Computer Science}
{IT project examples carried out during my university training:
\begin{itemize}\renewcommand{\labelitemi}{$\; \; \; \; \;   \circ$}	
	\item Development in C++ of meta-heuristics to solve the 2D bin packing problem under guillotine constraints.
	\item Development of the simplex algorithm in scilab.
	\item Decentralized chess game developed in Java with a group of \textit{23} people.
	%\item Development of a Gephi plugin to solve the multi-source vehicle routing problem with heuristics.
	\item Conception of a Tower Defense game in C++ and Qt.\newline
\end{itemize}
}
\cvline{June 2008}{\textbf{Baccalauréat S}, mathematics specialty, with honors in lycée \textsl{Fulbert} in Chartres.}

\section{Technical skills}

\cvline{Mathematics}{Graph theory, mathematical optimization, meta-heuristics, constrained programming,\newline Markov chain, distributed algorithm, basics in cryptography.}

\cvline{Computer}{ \vspace*{-0.25cm}
\begin{description}
\item[Programming:]{C++, Python, Prolog, Lisp,  PostgreSQL. Exploring: Rust and Scala.}
\item[Web:]{(x)HTML, JavaScript, CSS, PHP.}
\item[Software:]{Git/svn, Gephi/Tulip, Scilab, Prelude ERP, Witness.}
\item[Other:]{Agile software development, UML modeling, Linux server administration, \LaTeX.}
\end{description}\vspace*{-0.55cm}
}

\bibliographystyle{plain}
\bibliography{library.bib}
\bibentry{Gaumont2015}
\bibentry{Gaumont2014}
%\bibliographystyle{apalike}
%\bibliography{my.bib}

%\section{teaching}
%\cvline{bla bla}{blabla}


\section{Language skills}
%\cvline{French}{Mother tongue}{}
\cvline{English}{European level C1. Good working knowledge.\newline $\circ$ \textit{TOEIC score in 2012: 960/990}.}
\cvline{German}{European level B2. Reasonable working knowledge.}{}


\section{Interests}
\cvline{}{\small Open-source software (Mozilla), strong involvement in association, sport(bouldering, badminton), video-game.}


\end{document}


%% end of file `template_en.tex'.